---
title: "GH CEA Registry Dashboard"
#author: "Jojo Emerson"
#date: "October 25, 2018"
output: html_document
params:
  country: NA
  methods: NA
  ratios: NA
  countries: NA
  logo: NA
  logo2: NA
---

```{r, echo=FALSE, out.width="20%"}
library(knitr)
suppressWarnings(library(png))

  #logo as object
  logo_object <- readPNG(params$logo)
  knitr::include_graphics(params$logo)
    logo_object2 <- readPNG(params$logo2)
    knitr::include_graphics(params$logo2)
```

# Registry Contents for `r paste(params$country)`

```{r echo = FALSE} 
library(knitr)

    #Create vector of Registry contents for selected disease:
    # of studies and ratios, range of ICERs, # of interventions and countries
 
    #Number of studies
    num_studies<-nrow(params$methods)
    
    #Number of ratios
    num_ratios<-nrow(params$ratios)
    
    #Range of ICERs
     suppressWarnings({
      high_ICER<-max(params$ratios$NumericICER)
      high_ICER<-ifelse(high_ICER == -999999, "Cost-Saving", high_ICER)
      high_ICER<-ifelse(high_ICER == 9999999, "Dominated", high_ICER)
      low_ICER<-min(params$ratios$NumericICER)
      low_ICER<-ifelse(low_ICER == -999999, "Cost-Saving", low_ICER)
      low_ICER<-ifelse(low_ICER == 9999999, "Dominated", low_ICER)

      range_ICER<-paste(low_ICER,high_ICER, sep = " - ")
     })
   
   #Number of Interventons
   unique_interventions<-length(unique(params$ratios$InterventionPhrase))
   
   #Numer of diseases
    disease_specific_country<-
      rbind(as.data.frame(table(params$methods$GBDDis1_tier1)),
            as.data.frame(table(params$methods$GBDDis1_tier2)),
            as.data.frame(table(params$methods$GBDDis1_tier3)),
            as.data.frame(table(params$methods$GBDDis1_tier4)),
            as.data.frame(table(params$methods$GBDDis2_tier1)),
            as.data.frame(table(params$methods$GBDDis2_tier2)),
            as.data.frame(table(params$methods$GBDDis2_tier3)),
            as.data.frame(table(params$methods$GBDDis2_tier4)),
            as.data.frame(table(params$methods$GBDDis3_tier1)),
            as.data.frame(table(params$methods$GBDDis3_tier2)),
            as.data.frame(table(params$methods$GBDDis3_tier3)),
            as.data.frame(table(params$methods$GBDDis3_tier4)),
            as.data.frame(table(params$methods$GBDDis4_tier1)),
            as.data.frame(table(params$methods$GBDDis4_tier2)),
            as.data.frame(table(params$methods$GBDDis4_tier3)),
            as.data.frame(table(params$methods$GBDDis4_tier4)),
            as.data.frame(table(params$methods$GBDDis5_tier1)),
            as.data.frame(table(params$methods$GBDDis5_tier2)),
            as.data.frame(table(params$methods$GBDDis5_tier3)),
            as.data.frame(table(params$methods$GBDDis5_tier4)))
    unique_diseases_country<-length(unique(disease_specific_country$Var1))
   
```

Registry contents               |
--------------------------------|-------------------------------
Number of studies               |`r paste(num_studies)`
Number of ratios                |`r paste(num_ratios)`
Range of ICERs (2016 USD)       |`r paste(range_ICER)`
Number of unique interventions  |`r paste(unique_interventions)`
Number of unique diseases       |`r paste(unique_diseases_country)`

***
### Top 5 Selected Cost-Effective Interventions for `r paste(params$country)`

```{r echo = FALSE}
#order subsetted ratios from most to least cost effective
    ordered_ratios <- params$ratios[order(params$ratios$NumericICER),] 
    #reduce to only top 5
    ordered_ratios<-ordered_ratios[1:5,]
    #create output table format
    league_table<-data.frame(ordered_ratios$InterventionCombined, ordered_ratios$TargetPopulation, ordered_ratios$DisplayRatio, ordered_ratios$TitleAut)
    colnames(league_table)<-c("Intervention", "Target Population", "Cost/DALY averted", "Source (Title, Author)")

    kable(league_table)
    
```

***
### Density of Ratios by Intervention Types for `r paste(params$country)`

```{r echo = FALSE, message = FALSE}

library(plotly)
library(ggplot2)

params$ratios %>%
      group_by(Intervention1) %>%
      summarize(count = n()) %>%
      plot_ly(labels = ~Intervention1, values = ~count) %>%
      add_pie(hole = 0.6) %>%
      layout(showlegend = T,
             xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
             yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

```

***
### Distribution of CEAs by Disease Area for `r paste(params$country)`
```{r echo = FALSE, message = FALSE}

   #create dataframe
    treemap_data<-as.data.frame(table(params$methods$GBDDis1_tier2))
    colnames(treemap_data)<-c("Disease", "Number of CEAs")
    #rename diseases to shorthand
    treemap_data$disease_short[treemap_data$Disease == "Cardiovascular and circulatory diseases"]<-"Cardiovascular/circulatory"
    treemap_data$disease_short[treemap_data$Disease == "Chronic respiratory diseases"]<-"Chronic respiratory"
    treemap_data$disease_short[treemap_data$Disease == "Diabetes, urogenital, blood, and endocrine diseases"]<-"Diabetes and related"
    treemap_data$disease_short[treemap_data$Disease == "Diarrhea, lower respiratory infections, meningitis, and other common infectious diseases"]<-"Common infectious"
    treemap_data$disease_short[treemap_data$Disease == "Digestive diseases"]<-"Digestive"
    treemap_data$disease_short[treemap_data$Disease == "HIV/AIDS and tuberculosis"]<-"HIV/AIDS, TB"
    treemap_data$disease_short[treemap_data$Disease == "Maternal disorders"]<-"Maternal"
    treemap_data$disease_short[treemap_data$Disease == "Neoplasms"]<-"Neoplasms"
    treemap_data$disease_short[treemap_data$Disease == "Mental and behavioral disorders"]<-"Mental/behavioral"
    treemap_data$disease_short[treemap_data$Disease == "Musculoskeletal disorders"]<-"Musculoskeletal"
    treemap_data$disease_short[treemap_data$Disease == "Neglected tropical diseases and malaria"]<-"Neglected tropical"
    treemap_data$disease_short[treemap_data$Disease == "Neonatal disorders"]<-"Neonatal"
    treemap_data$disease_short[treemap_data$Disease == "Neurological disorders"]<-"Neurological"
    treemap_data$disease_short[treemap_data$Disease == "Nutritional deficiencies"]<-"Nutritional"
    treemap_data$disease_short[treemap_data$Disease == "Other communicable, maternal, neonatal, and nutritional disorders"]<-"Other communicable"
    treemap_data$disease_short[treemap_data$Disease == "Other non-communicable diseases"]<-"Other non-communicable"
    treemap_data$disease_short[treemap_data$Disease == "Self-harm and interpersonal violence"]<-"Violence"
    treemap_data$disease_short[treemap_data$Disease == "Transport injuries"]<-"Transport injury"
    treemap_data$disease_short[treemap_data$Disease == "Unintentional injuries other than transport injuries"]<-"Other injury"
    
    
    treemap_plot<-ggplot(treemap_data, aes(area = `Number of CEAs`, label = disease_short)) +
      geom_treemap(colour = 'white', fill = 'steelblue3')+geom_treemap_text(fontface = "italic", colour = "white", place = "centre", grow = TRUE, min.size = 2, reflow = T)
    
    treemap_plot
    
```

***
### Distribution of Ratios by CE Threshold* for `r paste(params$country)`

```{r echo = FALSE}

#create stacked bar dataframe
    R_CS<-sum(params$ratios$R_CS)
    R_LT1<-sum(params$ratios$R_LT1)
    R_1to3<-sum(params$ratios$R_1to3)
    R_GT3<-sum(params$ratios$R_GT3)
    R_D<-sum(params$ratios$R_D)
    Thresholds<-data.frame(R_CS, R_LT1, R_1to3, R_GT3,R_D)
    colnames(Thresholds)<-c("R_CS", "R_LT1", "R_1to3", "R_GT3", "R_D")
    
    #create ratios stacked bar chart, stratified by ratios
    stackedbar<-plot_ly(Thresholds, x = ~Thresholds, y = ~R_CS, type = 'bar', name = 'Cost-Saving', 
                        hoverinfo = "y") %>%
      add_trace(y = ~R_LT1, name = 'Less than 1x GDP') %>%
      add_trace(y = ~R_1to3, name = '1-3x GDP') %>%
      add_trace(y = ~R_GT3, name = 'Greater than 3x GDP') %>%
      add_trace(y = ~R_D, name = 'Dominated') %>%
      layout(yaxis = list(title = 'Number of cost/DALY averted ratios'),
             xaxis = list(title = "", showticklabels=FALSE),
             barmode = 'stack')

    stackedbar


```
* Although we categorize the ICERs based on country-specific GDP per capita to improve interpretability, we do not endorse any specific cost-effectiveness thresholds as reflective of good or reasonable value for money. More information [found here](http://healtheconomics.tuftsmedicalcenter.org/orchard/thresholds).

***
### Distribution of CEAs Published Over Time for `r paste(params$country)`
```{r echo = FALSE}

articlecount<-aggregate(params$methods$ArticleID, by = params$methods["PubYear"] , FUN = length)
      colnames(articlecount)<-c("Year", "Article Count")

      articlecount$Year <- factor(articlecount$Year)

      stackedbar <- plot_ly(articlecount, x = ~Year, y = ~`Article Count`, type = "bar",
                            marker = list(color = 'rgb(158,202,225)',
                                          line = list(color = 'rgb(8,48,107)', width = 1.0))) %>%
        layout(xaxis = list(title = "", showticklabels=TRUE),
               yaxis = list(title = "Number of cost/DALY CEAs"))
      
    stackedbar

```

